\subsection{\textit{A Wavelet-Based Dual
        Stream Network For Underwater Image Enhancement\cite{Ma_2022}}}

\paragraph{Abstract:}
This method enhances underwater images by applying a wavelet-based decomposition that separates structural and detail components. A dual-stream neural network then restores color and texture independently, and fuses them to generate high-quality results. The use of multi-color space fusion and GAN-based training improves realism and visual clarity.

\paragraph{Methodology:}
\begin{itemize}
    \item  \textbf{Wavelet Decomposition (DWT):} Splits the image into low- and high-frequency sub-bands (ILL, ILH, IHL, IHH).
    \item \textbf{Dual-Stream Network:}
          \begin{itemize}
              \item \textbf{Multi-color space fusion network:}  Enhances low-frequency ILL using color correction and multi-color space fusion.
              \item \textbf{Detail Branch:} Enhances high-frequency ILH, IHL, IHH sub-bands to recover texture and edges.
          \end{itemize}
    \item \textbf{Reconstruction (IDWT):} Merges enhanced sub-bands to produce the final output.
    \item \textbf{Training:} Uses combined L1 + MSSIM (structure), detail loss, and adversarial loss.
\end{itemize}

\paragraph{Advantages:}
\begin{itemize}
    \item Works well even on real-world underwater images.
    \item GAN improves visual realism.

\end{itemize}

\paragraph{Disadvantages:}
\begin{itemize}
    \item Computationally heavier due to dual networks and GAN.
    \item Requires a large dataset for robust training.
\end{itemize}