\subsection{\textit{IGFU: A Hybrid Underwater Image Enhancement Approach Combining Adaptive GWA, FFA-Net With USM\cite{Yuan_2025}}}

\paragraph{Abstract:}
This paper proposes a three-stage pipeline that combines an Improved Grey World Algorithm (IGWA), Feature Fusion Attention Network (FFA-Net) architecture, and Unsharp Masking (USM) to create a three-stage pipeline for enhancing underwater images.

\paragraph{Methodology:}
\begin{itemize}
      \item \textbf{Improved GWA}
            \begin{itemize}
                  \item GWA works on the principle that the average color in an image is gray. The colors are normalized between 0 to 1 and scaled up based on the mean gray value.
                  \item GWA can lead to overcorrection and cause the image to be too red.
                  \item Improved GWA makes minute changes based on channel-specific statistics alongside iterative retuning to prevent overcorrection.
            \end{itemize}

      \item \textbf{FFA-Net}
            \begin{itemize}
                  \item FFA-Net stands for Feature Fusion Attention Network.
                  \item It uses a deep learning model for dehazing the image.
                  \item The model has a channel and pixel attention module.
            \end{itemize}

      \item \textbf{USM}
            \begin{itemize}
                  \item Unsharp masking enhances details in the image.
                  \item It applies a Gaussian blur and subtracts the blurred image from the original image to obtain edges.
                  \item The edges are then added back to the original image.
            \end{itemize}
\end{itemize}

\paragraph{Advantages:}
\begin{itemize}
      \item \textbf{Hybrid Design} \\
            Both traditional and deep learning methods are used.

      \item \textbf{Adaptive Correction} \\
            Improved GWA algorithm corrects the image adaptively based on channel-specific statistics.

      \item \textbf{Component Modularity} \\
            Each component is a separate module and focuses on a different aspect of image enhancement.
\end{itemize}

\paragraph{Disadvantages:}

\begin{itemize}
      \item \textbf{Computational Complexity} \\
            High computational overhead due to multi-stage pipeline.

      \item \textbf{Requires Careful Tuning} \\
            Thresholds and coefficients are empirically determined.

      \item \textbf{Execution Time} \\
            Improved GWA requires iterative processing.

      \item \textbf{Artificial Edges} \\
            USM may amplify noise and introduce artificial edges.
\end{itemize}