\subsection{\textit{Intelligent Underwater Object Detection and Image Restoration for Autonomous Underwater Vehicles}\cite{Fayaz_2023}}

\paragraph{Abstract:}
This paper proposes a \textbf{two-stage framework} for AUVs:
\begin{itemize}
    \item \textbf{Object Detection:} Uses YOLOv8 for fast ROI detection (94.6% mAP).
    \item \textbf{Image Restoration:} A novel dehazing algorithm estimates per-channel transmission maps to reduce artifacts.
\end{itemize}
Achieves \textbf{UCIQE = 3.09} and \textbf{0.55s runtime}, enabling real-time underwater monitoring.

\paragraph{Methodology:}
\begin{itemize}
    \item \textbf{Detection Stage:}
          \begin{itemize}
              \item YOLOv8 processes images in \textbf{0.028ms} (compared to YOLOv4’s 94.35% mAP).
              \item Trained on a curated dataset including fish, divers, and submarines.
          \end{itemize}

    \item \textbf{Restoration Stage:}
          \begin{itemize}
              \item Estimates \textbf{transmission maps for RGB channels} separately.
              \item Uses \textbf{Underwater Dark Channel Prior (UDCP)} and guided filtering.
              \item Key equation:
                    \[
                        t_{bl}(e) = 1 - \left( \frac{\min_{c \in \{b,g\}}(\min_{y \in \pi(e)} I_c(y))}{c_{\text{err},g,b} A_{mc}} \right)
                    \]
          \end{itemize}
\end{itemize}

\paragraph{Advantages:}
\begin{itemize}
    \item \textbf{High accuracy:} 94.6% mAP for object detection.
    \item \textbf{Real-time performance:} 0.55s total processing time.
    \item \textbf{Robust dehazing:} Handles color distortion and scattering.
\end{itemize}

\paragraph{Disadvantages:}
\begin{itemize}
    \item \textbf{Prior dependency:} Restoration fails if transmission maps are inaccurate.
    \item \textbf{Limited depth testing:} Primarily validated at shallow depths (\textless5m).
\end{itemize}